R for Clinical Study Reports and Submission

### 2021-09-16 index.Rmd
address Aiming's comments

```{r, echo = FALSE}
contributors <- c(person("Yilong", "Zhang", email = "yilong.zhang@merck.com", role = "aut"), 
                  person("Nan", "Xiao", role = "aut"), 
                  person("Keaven", "Anderson", role = "aut"),
                  person("Yujie", "Zhao", role = "ctr"))
```

>>>>

```{r, echo = FALSE}
contributors <- c(person("Yilong", "Zhang", email = "yilong.zhang@merck.com", role = "aut"), 
                  person("Nan", "Xiao", role = "aut"), 
                  person("Keaven", "Anderson", role = "aut"),
                  person("Yujie", "Zhao", role = "ctr"), 
                  person("Aiming", "Yang", role = "ctr"))
```
